Introduction

### 2024-09-07 archive.qmd
Add appropriate attribution and license info

The project is now ready to be deposited for long-term archival. When considering an appropriate repository, there are a few questions to ponder [@Jackson2018]:

>>>>

The project is now ready to be deposited for long-term archival. When considering an appropriate repository, there are a few questions to ponder [excerpt from @Jackson2018, with footnotes removed, licensed under [CC\ BY\ 4.0](https://creativecommons.org/licenses/by/4.0/)]:

### 2024-09-07 intro.qmd
Add appropriate attribution and license info

Together, we will create a research compendium whilst taking the following ten things into account [@Arguillas2022]:

>>>>

Together, we will create a research compendium whilst taking the following ten things into account [by @Arguillas2022, licensed under [CC\ BY\ 4.0](https://creativecommons.org/licenses/by/4.0/)]:
